Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-28 paper.tex
clarify flows in case1

The large differences seen between monthly and quarterly time step cases in
Figures \ref{fig:unfueled} and \ref{fig:badshare} are
primarily caused by the \emph{inventory drawdown effect}.  Figure
\ref{fig:puinv} helps to visualize this effect.  The black dots in
the figure represent impulse flows of available Pu out of the fuel fab and
into fast reactors.  Blue lines represent the flows into Pu inventory
available for making fuel. The in flows are not shown for the individual
reactor cases because they are somewhat messy and obscure other information in
the plots. The colored curves show Pu inventory available for making fast
reactor fuel.  When the inventory curves meet and force down the flows, fuel
shortages occur.

Quarterly time steps have less frequent but larger impulse material flows.
These larger flows, however, do not compensate for the larger withdrawals
because facilities do not know about incoming inventory when they resolve
their outflow for a particular time step.  This information lag effectively
requires the floating Pu inventory to be maintained at a higher level during
the shortage.  This can be clearly seen in the case 4 plot which has a higher
standing inventory than case 2 during the fuel shortage years.  The case 4 Pu
inventory is unable to drop below approximately 100 tonnes, which indicates
out-flows to be roughly equal to the Pu flow into inventory each time step
during those years.  This can be confirmed by the in-flow and inventory curves
touching at those points.  Case 2 Pu inventory is similarly limited at about
the 30 tonne level.  As expected, the case 4 withdrawals are also three times
higher case 2 withdrawals.

@@

\begin{figure*}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv.eps}
    \caption[Separated Pu inventory and flow]{
        Separated Pu inventory and flows for all four cases.  In-flows for
        cases 1 and 3 are omitted because they are very noisy and obscure
        useful other information.  Larger time steps results in larger per
        time step material flows. These larger flows mean more material is not
        available for supplying to requesters.  This information lag causes
        more supply constraints than occur with smaller time steps -
        illustrating the \emph{inventory drawdown effect}.
    }
    \label{fig:puinv}
\end{figure*}

>>>>

The large differences seen between monthly and quarterly time step cases in
Figures \ref{fig:unfueled} and \ref{fig:badshare} are primarily caused by the
\emph{inventory drawdown effect}.  Figure \ref{fig:puinv} helps to visualize
this effect.  The black dots in the figure represent impulse flows of
available Pu out of the fuel fab and into fast reactors.  Blue lines represent
the flows into Pu inventory available for making fuel. The in flows are not
shown for the individual reactor cases because they are somewhat messy and
obscure other information in the plots. The colored curves show Pu inventory
available for making fast reactor fuel.  When the inventory curves meet and
force down the out-flows, fuel shortages occur.  While this is most clear for
cases 2 and 4, the individual reactor scenarios (cases 1 and 3) also have many
points during the shortage where the outflow point lies exactly on top of the
inventory point - indicating that all available inventory is being
transferred.

Quarterly time steps have less frequent but larger impulse material flows.
These larger flows, however, do not compensate for the larger withdrawals
because facilities do not know about incoming inventory when they resolve
their outflow for a particular time step.  This information lag effectively
requires the floating Pu inventory to be maintained at a higher level during
the shortage.  This can be clearly seen in the case 4 plot which has a higher
standing inventory than case 2 during the fuel shortage years.  The case 4 Pu
inventory is unable to drop below approximately 100 tonnes, which indicates
out-flows to be roughly equal to the Pu flow into inventory each time step
during those years.  This can be confirmed by the in-flow and inventory curves
touching at those points.  Case 2 Pu inventory is similarly limited at about
the 30 tonne level.  As expected, the case 4 withdrawals are also three times
higher case 2 withdrawals exactly matching the time step duration ratio
between the two cases.

@@

The striations visible in the monthly flows for case 1 in Figure
\ref{fig:puinv} are a characteristic of the synchronization of reactor
refueling caused by the shortage.  They are a sort of resonances of that the
inventory level jumps between, and they gradually disappear as the refueling
cycles become more staggered.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv.eps}
    \caption[Separated Pu inventory and flow]{

        Separated Pu inventory and flows for all four cases.  In-flows for
        cases 1 and 3 are omitted because they are noisy and obscure other
        useful information.  A larger time step results in larger per time
        step material flows. These larger flows mean more material is not
        available for supplying to requesters.  This information lag causes
        more supply constraints than occur with smaller time steps -
        illustrating the \emph{inventory drawdown effect}. Another result of
        this effect is the larger standing Pu inventory during the shortage
        with larger time steps that can be seen in case 4 than in case 2.

    }
    \label{fig:puinv}
\end{figure*}
